Verifying Demonstrations

### 2017-11-16 contents-poster.tex
Adds logos
Adds QR-code, fixes spacing for logos
Adds some conclusions

\begin{center}
  \Huge\bfseries
  Securely and Privately Verifiable Protests
\end{center}
\begin{center}
  \large
  Daniel Bosk $\bullet$ Sonja Buchegger $\bullet$ Sébastien Gambs
\end{center}
\vspace{1.5em}

@@

    \begin{purpleblock}{Conclusions}
      \begin{itemize}
        \item \dots
      \end{itemize}
    \end{purpleblock}

@@

>>>>

\begin{columns}
  \begin{column}{0.17\linewidth}
    \includegraphics[width=0.5\linewidth]{fig/kth_cmyk.eps}
    \hfill
  \end{column}
  \hfill
  \begin{column}{0.64\linewidth}
    \begin{center}
      \Huge\bfseries
      Securely and Privately Verifiable Protests
    \end{center}
    \begin{center}
      \large
      Daniel Bosk <dbosk@kth.se>
      $\bullet$
      Sonja Buchegger
      $\bullet$
      Sébastien Gambs
    \end{center}
    \vspace{1.5em}
  \end{column}
  \hfill
  \begin{column}{0.17\linewidth}
    \hfill
    \includegraphics[width=0.8\linewidth]{fig/uqam.pdf}
  \end{column}
\end{columns}

@@

    \begin{purpleblock}{Conclusions}
      \begin{itemize}
        \item Provides a \emph{lower bound} of the participation count.
        \item Provides a verifiable participation count, as strong as the 
          blockchain is immutable.
        \item Provides privacy based on anonymous credentials.
        \item The only added risk (over not using this) is if someone can use 
          your secret key (\(k_P\)).
        \item Requires only local connectivity during the protest.
      \end{itemize}
    \end{purpleblock}

@@

    %\vspace{10cm}
    \begin{center}
      \includegraphics[width=0.5\linewidth]{fig/qr.eps}
    \end{center}
